---
title: "Transmission Risk Comparison"
author: "Remo Schmutz"
date: "2022-12-21"
output:
  pdf_document: default
  html_document: default
  keep_md: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)
knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      cache = TRUE)
```

## Libraries 

```{r libraries}
library(tidyverse)
library(ggplot2)
require("knitr")
library(gridExtra)
library(grid)
library(lubridate)
library(dplyr)
library(hms)
library(truncdist)
library(crch)
library(stats)
library(LaplacesDemon)
library(ggstatsplot)
library(MASS)
library(fitdistrplus)
library(truncnorm)
library(tidybayes)
library(ggpubr)
library(psych)
library(ggpattern)
library(gridExtra)
library(GGally)

text_size = 8
theme_bw2 <- function () { 
  theme_bw(base_size = text_size, base_family = 'sans') %+replace% 
    theme(
      axis.text = element_text(size = text_size),
      axis.title = element_text(size = text_size),
      plot.title = element_text(size = text_size + 2, face = "bold", hjust = 0, margin = ggplot2::margin(0, 0, 5, 0))
    )
}


```

## Data 

```{r data import}
ch <- readRDS("data-clean/co2-ch.rds") #swiss data
satz <- readRDS("data-clean/co2-sa-tz.rds")

ch <- ch %>% 
  filter(co2 > 400) %>% 
  arrange(co2)

ch1 <- ch %>% 
  filter(school == "School 1") 

ch2 <- ch %>% 
  filter(school == "School 2")

sa <- satz %>% 
  filter(country == "South Africa") %>% 
  filter(co2 < 3000) %>% 
  filter(co2 > 400) %>% 
  arrange(co2)#south africa data

tz <- satz %>% 
  filter(country == "Tanzania") %>% 
  filter(co2 < 3000) %>%
  filter(co2 > 400) %>% 
  mutate(time_h = hour(date)) %>% 
  filter(time_h >= 8) %>% 
  arrange(co2) #tanzania data

```

## Methods

Indoor Co2 concentration \
  * mean or distribution from data<br> \
* $C_o:=$ Outdoor Co2 concentration<br>
  * from literature https://www.fsis.usda.gov/sites/default/files/media_file/2020-08/Carbon-Dioxide.pdf \
* $C_a:=$ Volume fraction of CO2 added to exhaled breath during breathing \
  * Persily and de Jonge [Table 3 and 4] doi: 10.1111/ina.12383 \
* $\bar{f}:=$ $\int_{t=0}^{t=max}f dt$ \
  * integrating over f values from different times $(2)$ or using a distribution based on the data \
* $I:=$ Number of infectors in the class \
  * estimated using prevalence of the age group in the country \
* $q:=$ Quantum per hour \
  * assuming a distribution from literature \
* $t:=$ time \
  * changing this parameter to compare \
* $n:=$ number of people in the class \
  * data (Switzerland) or assumption (South Africa, Tanzania) \

## Preprocess

```{r preprocess}
ch_hourly <- ch %>%
  mutate(time_h = hour(time)) %>%
  group_by(school, time_h) %>%
  summarize(mean = mean(co2),
            lower = quantile(co2, 0.25),
            upper = quantile(co2, 0.75),
            n_data = n()) %>%
  ungroup()

ch_hourly %>%
  ggplot(aes(x = time_h, y = n_data, fill = school)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  xlab("Daytime (h)") +
  ylab("number of measurements") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank()) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2")
# there is a reasonable number of data points per hour but missing data at hour 12 for school 2 (no lessons)

tz_hourly <- tz %>%
  mutate(time_h = hour(date)) %>%
  group_by(time_h) %>%
  summarize(mean = mean(co2),
            lower = quantile(co2, 0.25),
            upper = quantile(co2, 0.75),
            n_data = n()) %>%
  ungroup()

tz_hourly %>%
  ggplot(aes(x = time_h, y = n_data)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  xlab("Daytime (h)") +
  ylab("number of measurements") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank())

# data is measured throughout the day in south africa

```

## Analysis 

### Co2 over time 

```{r}
ch_hourly %>% #plot co2 during the day (ch)
  ggplot(aes(x = time_h, group = school, color = school)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .2, position =    position_dodge2(width = .2)) +
  geom_point(aes(y = mean), position = position_dodge2(width = .2)) +
  scale_color_brewer(palette = "Set2") +
  scale_x_continuous(breaks = seq(7, 16, 1)) +
  labs(x = "Daytime (h)", y = "CO2 (Mean and IQR)") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank()) 

tz_hourly %>% #plot co2 during the day (tz)
  ggplot(aes(x = time_h)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .2, position =    position_dodge2(width = .2)) +
  geom_point(aes(y = mean), position = position_dodge2(width = .2)) +
  scale_color_brewer(palette = "Set2") +
  scale_x_continuous(breaks = seq(7, 17, 1)) +
  labs(x = "Daytime (h)", y = "CO2 (Mean and IQR)") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank()) 

#no time data available for south africa
```

### Smoothing Data

```{r}
# CH
##school 1
set.seed(1)

dat_ch1 <- data.frame(
  x = 1:length(ch1$co2),
  y = ch1$co2
)

loessData_ch1 <- data.frame(
  x = 1:length(ch1$co2),
  y = predict(loess(y~x, dat_ch1, span = 0.1)),
  method = "loess()"
) %>% 
  mutate(school = "school 1")

ggplot(loessData_ch1, aes(x, y)) + 
  geom_point(dat = dat_ch1, aes(x, y), alpha = 0.2, col = "red") +
  geom_line(col = "blue") +
  facet_wrap(~method) +
  theme_bw(16)

##school 2
dat_ch2 <- data.frame(
  x = 1:length(ch2$co2),
  y = ch2$co2
)

loessData_ch2 <- data.frame(
  x = 1:length(ch2$co2),
  y = predict(loess(y~x, dat_ch2, span = 0.3)),
  method = "loess()"
) %>% 
  mutate(school = "school 2")

ggplot(loessData_ch2, aes(x, y)) + 
  geom_point(dat = dat_ch2, aes(x, y), alpha = 0.2, col = "red") +
  geom_line(col = "blue") +
  facet_wrap(~method) +
  theme_bw(16)

loessData_ch <- rbind(loessData_ch1,loessData_ch2)

# TZ
dat_tz <- data.frame(
  x = 1:length(tz$co2),
  y = tz$co2
)

loessData_tz <- data.frame(
  x = 1:length(tz$co2),
  y = predict(loess(y~x, dat_tz, span = 0.3)),
  method = "loess()"
)

ggplot(loessData_tz, aes(x, y)) + 
  geom_point(dat = dat_tz, aes(x, y), alpha = 0.2, col = "red") +
  geom_line(col = "blue") +
  facet_wrap(~method) +
  theme_bw(16)

# SA
dat_sa <- data.frame(
  x = 1:length(sa$co2),
  y = sa$co2
)

loessData_sa <- data.frame(
  x = 1:length(sa$co2),
  y = predict(loess(y~x, dat_sa, span = 0.3)),
  method = "loess()"
)

ggplot(loessData_sa, aes(x, y)) + 
  geom_point(dat = dat_sa, aes(x, y), alpha = 0.2, col = "red") +
  geom_line(col = "blue") +
  facet_wrap(~method) +
  theme_bw(16)

```

### Co2 distribution of smoothed data

```{r}
loessData_ch %>% #density plot ch
  ggplot(aes(x = y, color = school, fill = school)) +
  geom_density(alpha = .2, kernel = "gaussian", adjust = 3) +
  scale_x_continuous(expand = c(0,0)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)),limits = c(0, 0.004)) +
  scale_x_continuous(limits = c(400, 3000)) +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank()) +
  ggtitle("Probability distribution of observed Co2-values (Switzerland)")

loessData_sa %>% #density plot sa smooth
  ggplot(aes(x = y)) +
  geom_density(alpha = .2, kernel = "gaussian", adjust = 4, fill = "darkseagreen3") +
  scale_x_continuous(expand = c(0,0)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(limits = c(0, 0.002)) +
  scale_x_continuous(limits = c(400, 3000)) +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme(legend.position = "none") +
  theme_bw2() 

loessData_tz %>% #density plot tz smooth
  ggplot(aes(x = y)) +
  geom_density(alpha = .2, kernel = "gaussian", adjust = 3.2) +
  scale_x_continuous(expand = c(0,0)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(limits = c(0, 0.0075)) +
  scale_x_continuous(limits = c(400, 3000)) +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme_bw2() +
  theme(legend.position = c(0.9,0.9), legend.title = element_blank()) 
```
### Distribution co2

```{r distribution for co2 ch1}
#C_a
C_a <- ((0.0042)*60)/8 #https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5666301/ mean girls (11-16 and 16-21), boys (11-16 and 16-21) for co2 production rate per minute, the breathing rate (8) comes from Rudnick paper

#C_o
C_o <- 400 #p.p.m (taking a higher estimate because higher values ar possible when a lot of traffic ect.)
## all schools are directly on the side of a road (no info for tanzania), so i won't make a distinction

#school1
x_ch1 <- ch %>% 
  filter(school == "School 1") %>% 
  pull(co2)

descdist(x_ch1, discrete = FALSE) #normal distribution fits well
fitdistr(x_ch1, "gamma") #get parameters

x <- seq(400, 3000, by = .1)

co2_distr_ch1 <- data.frame(co2 = seq(400, 3000, .1)) %>% 
  mutate(prob = dtrunc(co2, spec = "gamma", a = 400, b = 3000, shape = 15.5, rate = 0.017)) %>%
  mutate(country = "Switzerland 1")

co2_distr_ch1 %>% 
  ggplot(aes(x=x,y=prob)) +
  geom_line(color= "red") +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme_bw2() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), limits = c(0, 0.004))  +
  scale_x_continuous(limits = c(400, 3000))

sample_co2_ch1 <- sample(co2_distr_ch1$co2, 10000, replace = TRUE, prob = co2_distr_ch1$prob) #sample co2 sample f
sample_f_ch1 <- tibble(co2 = sample_co2_ch1, f = ((co2-C_o)/C_a)/1000000) %>% #sample f for df_ch1
  dplyr::select(-co2)

####histogram / density comparison
hist(loessData_ch1$y, # histogram
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = expression(CO[2]*" (ppm)"),
 main = "",
 breaks = 7,
 xlim = c(400,1800),
 ylim = c(0,0.003))
lines(co2_distr_ch1, # density plot
 lwd = 2, # thickness of line
 col = "chocolate3")

```

```{r distribution for co2 ch2}
#school 2
x_ch2 <- loessData_ch2 %>% 
  pull(y) #pull filtered data

descdist(x_ch2, discrete = FALSE) #gamma fits ok 
fitdistr(x_ch2, "gamma") #get parameters

co2_distr_ch2 <- data.frame(co2 = seq(400, 3000, .1)) %>% #create data frame
  mutate(prob = dtrunc(x, spec = "gamma", a = 400, b = 3000, shape = 6.55, rate = 0.006)) %>% 
  mutate(country = "Switzerland 2")
#7.4
co2_distr_ch2 %>% #plots density
  ggplot(aes(x=x,y=prob)) +
  geom_line(color= "red") +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme_bw2() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), limits = c(0, 0.004))  +
  scale_x_continuous(limits = c(400, 3000))

sample_co2_ch2 <- sample(co2_distr_ch2$co2, 10000, replace = TRUE, prob = co2_distr_ch2$prob) #sample
sample_f_ch2 <- tibble(co2 = sample_co2_ch2, f = ((co2-C_o)/C_a)/1000000) %>%  #sample f for df_ch2
  dplyr::select(-co2)

####histogram / density comparison
hist(loessData_ch2$y, # histogram
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = expression(CO[2]*" (ppm)"),
 main = "",
 breaks = 7,
 xlim = c(400,2500),
 ylim = c(0,0.0015))
lines(co2_distr_ch2, # density plot
 lwd = 2, # thickness of line
 col = "chocolate3")

```

```{r distribution for co2 tz}
#tanzania
x_tz <- loessData_tz %>% 
  pull(y)

x_tz <- as.numeric(x_tz)

descdist(x_tz, discrete = FALSE, boot = 100) #gamma fits ok
fitdistr(x_tz, "t") #get parameters

co2_distr_tz <- data.frame(co2 = seq(400, 3000, .1)) %>% 
  mutate(prob = dtrunc(x, spec = "st", a = 400, b = 3000, mu = 593.95, sigma = 80, nu = 1.55)) %>% mutate(country = "Tanzania")

plot_co2_tz <- co2_distr_tz %>% 
  ggplot(aes(x=x,y=prob)) +
  geom_line(color= "red") +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  ggtitle("Tanzania") +
  theme_bw2() +
  scale_y_continuous(limits = c(0, 0.0075)) +
  scale_x_continuous(limits = c(400, 3000))

sample_co2_tz <- sample(co2_distr_tz$co2, 10000, replace = TRUE, prob = co2_distr_tz$prob) #sample
sample_f_tz <- tibble(co2 = sample_co2_tz, f = ((co2-C_o)/C_a)/1000000) %>% #sample f for df_tz
  dplyr::select(-co2)

####histogram / density comparison
hist(loessData_tz$y, # histogram
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = expression(CO[2]*" (ppm)"),
 main = "",
 breaks = 14,
 xlim = c(400, 1600),
 ylim = c(0,0.006))
lines(co2_distr_tz, # density plot
 lwd = 2, # thickness of line
 col = "chocolate3")

```


```{r distribution for co2 sa}
#south africa
x_sa <- loessData_sa %>% 
  pull(y)

x_sa <- as.numeric(x_sa)

descdist(x_sa, discrete = FALSE) #normal/gamma fits ok -> after comparison --> gamma is better
fitdistr(x_sa, "gamma") #get parameters

co2_distr_sa <- data.frame(co2 = seq(400, 3000, .1)) %>% 
  mutate(prob = dtrunc(x, spec = "gamma", a = 400, b = 3000, shape = 5.72, rate = 0.0039)) %>% 
  mutate(country = "South Africa")

co2_distr_sa %>% 
  ggplot(aes(x=x,y=prob)) +
  geom_line(color= "red") +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  ggtitle("South Africa") +
  theme_bw2() +
  scale_y_continuous(limits = c(0, 0.002)) +
  scale_x_continuous(limits = c(400, 3000))

sample_co2_sa <- sample(co2_distr_sa$co2, 10000, replace = TRUE, prob = co2_distr_sa$prob) #sample
sample_f_sa <- tibble(co2 = sample_co2_sa, f = ((co2-C_o)/C_a)/1000000) %>% #sample f for df_sa
  dplyr::select(-co2)

####histogram / density comparison
hist(loessData_sa$y, # histogram
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = expression(CO[2]*" (ppm)"),
 breaks = 10, 
 main = "",
 xlim = c(400, 3000),
 ylim = c(0,0.001))
lines(co2_distr_sa, # density plot
 lwd = 2, # thickness of line
 col = "chocolate3")

```

```{r plot co2}
##parameters: co2
co2_data <- rbind(co2_distr_ch1,co2_distr_ch2,co2_distr_sa,co2_distr_tz)

co2_data %>% 
  ggplot(aes(x=co2, y = prob, color = country)) +
  geom_line() +
  labs(x = expression(CO[2]*" (ppm)"), y = "Density") +
  theme_bw2() +
  scale_y_continuous(limits = c(0, 0.005)) +
  scale_x_continuous(limits = c(400, 3000)) +
  scale_color_discrete(name=NULL)

text_size = 8

```

## Quanta

I'll use the following studies for calculating the meanparameter: <br>

  Riley (1962): 130 patients, q: 1.25 <br>
  Escombe (2008): 117 patients, q: 8.2 <br>
  Nardell (1991) : 1 patients, q: 12.5 <br>
  Andrews (2014) : 571 patients, q: 0.89 <br>

```{r quanta tb}

q <- (1.25*130+8.2*117+12.5+0.89*571)/(130+117+1+571) #weighted mean from different studies

#Escombe Table 2
mean_one_inf <- mean(c(12,3,5.5,1.8,18,12)) #mean quanta of pers. which infected one pig
mean_two_inf <- mean(c(2.9,40)) #mean quanta of pers. which infected two pigs

q_inf_persons <- c(12,3,2.9,5.5,1.8,18,40,12,226,52,mean_two_inf,rep(mean_one_inf,11)) #asumed one infection p.p. for the remaining infected pigs
q_sample_total_norm <- c(q_inf_persons, rtruncnorm(117-length(q_inf_persons), a = 0, mean = 1, sd = 1))

fitdistr(q_sample_total_norm, "t") #get parameters

dq <- function(x) {
  dtrunc(x, spec = "st", a = 0, b = 300, mu = 1, sigma = 0.67, nu = 0.90) #parameters from fitdistr
}

rq_distr <- data.frame(quanta = seq(0, 300, .1)) %>% 
  mutate(prob = dq(quanta)) %>% 
  mutate(type = "TB")

rq_distr %>% 
  ggplot(aes(x = quanta, y = prob)) +
  geom_line()+
  theme_bw2() +
  xlab("Quanta") +
  ylab("Density")#Distribution of the quanta model

sample_q <- sample(rq_distr$quanta, 10000, replace = TRUE, prob = rq_distr$prob) #sample q for calculation later

tb_sample <- tibble(sample = sample_q) %>% 
  count(sample > 10) %>% 
  mutate(prob = n/10000) #what is the ratio of datapoints over 10?

q_under_10 <- tb_sample[1,3, drop = TRUE]
q_under_10 # approx. 96% of data points are below 10

mean(sample_q) #mean of the sample should be between 2 and 3
plot(sample_q, ylab="Quanta", xlab = "Sample", cex.axis=.7, cex.lab=.7)

thousand_sample <- replicate(10000, mean(sample(rq_distr$quanta, 1000, replace = TRUE, prob = rq_distr$prob))) 
#for calculating the distribution of the mean over lots of simulations
ggplot() + geom_density(mapping = aes(thousand_sample), alpha = .2, kernel = "gaussian", adjust = 5) +
  xlab("Mean of simulated q-value") +
  ylab("Density") +
  theme_bw2()
#Mean is in the desired area

```

```{r quanta covid}
## Buonanno et al. provide an estimation for the quanta (like in MCID)
#"light activity, speaking"
cov_q <- function(x) {
  dtrunc(x, spec = "lnorm", a = 0, meanlog = 0.698, sdlog = 0.720)
}

cov_q_distr <- data.frame(quanta = seq(0, 25, .1)) %>% 
  mutate(prob = cov_q(quanta)) %>% 
  mutate(type = "SARS")

cov_q_distr %>% 
  ggplot(aes(x = quanta, y = prob)) +
  geom_line() + 
  theme_bw2() +
  ylab("Density") +
  xlab("Quanta")

sample_q_cov <- sample(cov_q_distr$quanta, 10000, replace = TRUE, prob = cov_q_distr$prob)
```

```{r plot Quanta}
q_data <- rbind(rq_distr,cov_q_distr)

q_data %>% 
  ggplot(aes(x=quanta, y = prob, color = type)) +
  geom_line() +
  labs(x = "Quanta (q/h)", y = "Density") +
  theme_bw2() +
  scale_y_continuous(limits = c(0, 0.700)) +
  scale_x_continuous(limits = c(0, 25)) +
  scale_color_discrete(name=NULL) +
  geom_vline(xintercept = 1.25, linetype = "dashed", size = 0.2) +
  geom_vline(xintercept = 12.5, linetype = "dashed", size = 0.2) +
  geom_vline(xintercept = 8.2, linetype = "dashed", size = 0.2) +
  geom_vline(xintercept = 0.89, linetype = "dashed", size = 0.2) +
  annotate("text", x=13, y=0.65, label="Nardell", angle=90) +
  annotate("text", x=8.7, y=0.65, label="Escombe", angle=90) +
  annotate("text", x=1.7, y=0.65, label="Riley", angle=90) +
  annotate("text", x=0.45, y= 0.65, label="Andrews", angle=90)
  
```
## Rest of the parameters

```{r parameters}
#n
n_ch <- 20
n_sa <- 30 #Powerpoint
n_tz <- 50 #Powerpoint

#I tuberculosis
prev_ch <- 4.1/100000
#https://www.bag.admin.ch/bag/de/home/zahlen-und-statistiken/zahlen-zu-infektionskrankheiten.exturl.html/aHR0cHM6Ly9tZWxkZXN5c3RlbWUuYmFnYXBwcy5jaC9pbmZyZX/BvcnRpbmcvZGF0ZW5kZXRhaWxzL2QvdHViZXJrdWxvc2UuaHRt/bD93ZWJncmFiPWlnbm9yZQ==.html

prev_sa <- 513/100000
# tendenziell zu hoch da 15-25
 #https://worldhealthorg.shinyapps.io/tb_profiles/?_inputs_&entity_type=%22country%22&lan=%22EN%22&iso2=%22ZA%22 von Abbildung abgelesen (kids) 5-14 und 15-24
# Ansteckungen in Altersgruppe 5-24 durch Population in dieser Altersgruppe (nicht 15-24 genommen, da sonst eher zu hoch weil Inzidenz dann ab 20 stark steigt)
prev_tz <- 208/100000
#https://data.worldbank.org/indicator/SH.TBS.INCD?locations=TZ

I_ch <- prev_ch*n_ch #prevalence per class (per year)
I_sa <- prev_sa*n_sa
I_tz <- prev_tz*n_tz

#I Covid
I_ch_cov <- 0.05*n_ch
40000/8700000

month <- 7*5*4
year <- 7*5*4*10

#Covid 
##Excess mortality nicht mehr berücksichtigen
#Ratio between excess mortality rate and reported COVID-19 mortality rate
#CH: 1.29
#SA: 3.31
#TZ: 178.81

# Anzahl Excess mortality ist über den ganzen Zeitraum 19/20 berichtet, wenn ich einfach den Durchscnitt nehme, verliere ich die Varianz zwischen akuten Phasen und weniger ansteckenden Phasen.
#Nehme nun die ratio, wende Sie an die WHO Daten an und erhalte korrekte Anzahl Tote pro Zeitpunkt,
#mithilfe eines Estimators für IFR kann ich dann die Anzahl cases t-14 berechnen.

#IFR: https://www.eurosurveillance.org/docserver/fulltext/eurosurveillance/27/7/eurosurv-27-7-2.pdf?expires=1676535817&id=id&accname=guest&checksum=5C476EBB07761114ED0CE78E371DF5A7

#Excess: https://www.thelancet.com/action/showPdf?pii=S0140-6736%2821%2902796-3
#(((mean(635,635,630)*1.29)/0.005)/8600000)*n_ch
#(((mean(3649,4027,3723)*3.31)/0.005)/59400000)*n_sa
#(((mean(29,28,27)*178.81)/0.005)/63400000)*n_tz

I_ch_high <- (250000/8654622)*n_ch #https://covid19.who.int/region/euro/country/ch
I_sa_high <- (135000/59308690)*n_sa
I_tz_high <- (20000/45741007)*n_tz #data from uganda
#https://www.worldometers.info/world-population/population-by-country/ for the population

I_ch_medium <- (50000/8654622)*n_ch
I_sa_medium <- (50000/59308690)*n_sa
I_tz_medium <- (10000/45741007)*n_tz

I_ch_low <- (5000/8654622)*n_ch
I_sa_low <- (10000/59308690)*n_sa
I_tz_low <- (1000/45741007)*n_tz
```

```{r plot other parameters}
I_data <-tibble(country= c(rep(c("Switzerland", "South Africa", "Tanzania"), 4)), I = c(I_ch,I_sa,I_tz, I_ch_high, I_sa_high, I_tz_high, I_ch_medium, I_sa_medium, I_tz_medium, I_ch_low, I_sa_low, I_tz_low), type = c("TB", "TB", "TB", "SARS_high", "SARS_high", "SARS_high", "SARS_medium", "SARS_medium", "SARS_medium", "SARS_low", "SARS_low", "SARS_low" ))

I_data$type <- factor(I_data$type,
                      levels = c("TB", "SARS_high", "SARS_medium", "SARS_low"))

I_data %>% 
  group_by (country, type)%>%
  ggplot +
  geom_col(aes(x=country, y= I, fill=type), position = position_dodge(1))+
  theme_bw2()+
  theme(axis.title.x = element_blank())+
  labs(y = "Infectious persons per class") +
  scale_fill_discrete(name=NULL)
  

n_data <- tibble(country = c("Switzerland", "South Africa", "Tanzania"), n = c(n_ch, n_sa, n_tz)) 

n_data %>% 
  ggplot +
  geom_col(aes(x=country, y= n, fill = country), position = position_dodge(1))+ 
  theme_bw2()+
  theme(axis.title.x = element_blank()) +
  labs(y = "Class size") +
  scale_fill_discrete(name=NULL)

#https://coronavirus.jhu.edu/data/mortality
```


```{r preparing}
#preparing datasets for plotting
df_ch1 <- tibble(school = c(rep("school 1", 10000)), f = sample_f_ch1, q_tb = sample_q, q_cov = sample_q_cov) %>% 
  mutate(P_year = 1 - exp(-(f*I_ch*q_tb*year)/n_ch)) %>% 
  mutate(P_year_one = 1 - exp(-(f*1*q_tb*year)/n_ch)) %>% 
  mutate(P_month_one_cov = 1 - exp(-(f*1*q_cov*month)/n_ch)) %>% 
  mutate(P_month_est_high = 1 - exp(-(f*I_ch_high*q_cov*month)/n_ch)) %>% 
  mutate(P_month_est_medium = 1 - exp(-(f*I_ch_medium*q_cov*month)/n_ch)) %>% 
  mutate(P_month_est_low = 1 - exp(-(f*I_ch_low*q_cov*month)/n_ch))

df_ch2 <- tibble(school = c(rep("school 2", 10000)), f = sample_f_ch2, q_tb = sample_q, q_cov = sample_q_cov) %>% 
  mutate(P_year = 1 - exp(-(f*I_ch*q_tb*year)/n_ch)) %>% 
  mutate(P_year_one = 1 - exp(-(f*1*q_tb*year)/n_ch)) %>% 
  mutate(P_month_one_cov = 1 - exp(-(f*1*q_cov*month)/n_ch)) %>% 
  mutate(P_month_est_high = 1 - exp(-(f*I_ch_high*q_cov*month)/n_ch)) %>% 
  mutate(P_month_est_medium = 1 - exp(-(f*I_ch_medium*q_cov*month)/n_ch)) %>%
  mutate(P_month_est_low = 1 - exp(-(f*I_ch_low*q_cov*month)/n_ch)) 
  
df_tz <- tibble(school = c(rep("tanzania", 10000)), f = sample_f_tz, q_tb = sample_q, q_cov = sample_q_cov) %>% 
  mutate(P_year = 1 - exp(-(f*I_tz*q_tb*year)/n_tz)) %>% 
  mutate(P_year_one = 1 - exp(-(f*1*q_tb*year)/n_tz)) %>% 
  mutate(P_month_one_cov = 1 - exp(-(f*1*q_cov*month)/n_tz)) %>% 
  mutate(P_month_est_high = 1 - exp(-(f*I_tz_high*q_cov*month)/n_tz)) %>% 
  mutate(P_month_est_medium = 1 - exp(-(f*I_tz_medium*q_cov*month)/n_tz)) %>% 
  mutate(P_month_est_low = 1 - exp(-(f*I_tz_low*q_cov*month)/n_tz)) 

df_sa <- tibble(school = c(rep("south africa", 10000)), f = sample_f_sa, q_tb = sample_q, q_cov = sample_q_cov) %>% 
  mutate(P_year = 1 - exp(-(f*I_sa*q_tb*year)/n_sa)) %>% 
  mutate(P_year_one = 1 - exp(-(f*1*q_tb*year)/n_sa)) %>% 
  mutate(P_month_one_cov = 1 - exp(-(f*1*q_cov*month)/n_sa)) %>% 
  mutate(P_month_est_high = 1 - exp(-(f*I_sa_high*q_cov*month)/n_sa)) %>% 
  mutate(P_month_est_medium = 1 - exp(-(f*I_sa_medium*q_cov*month)/n_sa)) %>% 
  mutate(P_month_est_low = 1 - exp(-(f*I_sa_low*q_cov*month)/n_sa)) %>% 
  mutate(five_quantil = unname(quantile(P_year$f, probs = seq(0, 1, 1/20)))[2]) %>% 
  mutate(ninefive_quantil = unname(quantile(P_year$f, probs = seq(0, 1, 1/20)))[20])

df_complet <- bind_rows(df_ch1, df_ch2, df_sa, df_tz)

mean_tb_ch1 <- describe(df_ch1$P_year$f)
mean_tb_ch2 <- describe(df_ch2$P_year$f)
mean_tb_tz <- describe(df_tz$P_year$f)
mean_tb_sa <- describe(df_sa$P_year$f)

mean(df_tz$P_month_est_low$f)
median(df_tz$P_year$f)
```

## Plots of the transmission risk 

```{r plotting TB}
df_complet %>% 
  ggplot(aes(x = school, y=P_year$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.025,0.05,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1), trans = "sqrt")+
  xlab("Country") + 
  ylab("Yearly risk of infection") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_year$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_year$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_year$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_year$f, probs = 0.95))),colour="grey")
 
df_complet %>% 
 ggplot(aes(x = school, y=P_year_one$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.05,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1), trans = "exp")+
  xlab("Country") + 
  ylab("Yearly risk of infection") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_year_one$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_year_one$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_year_one$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_year_one$f, probs = 0.95))),colour="grey")

```

```{r plotting SARS}
df_complet %>% 
  ggplot(aes(x = school, y=P_month_one_cov$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))+
  xlab("Country") + 
  ylab("Monthly risk of infection") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_month_one_cov$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_month_one_cov$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_month_one_cov$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_month_one_cov$f, probs = 0.95))),colour="grey")

df_complet %>% 
  ggplot(aes(x = school, y=P_month_est_high$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))+
  xlab("Country") + 
  ylab("Monthly risk of infection)") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_month_est_high$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_month_est_high$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_month_est_high$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_month_est_high$f, probs = 0.95))),colour="grey")

df_complet %>% 
  ggplot(aes(x = school, y=P_month_est_medium$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))+
  xlab("Country") + 
  ylab("Monthly risk of infection)") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_month_est_medium$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_month_est_medium$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_month_est_medium$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_month_est_medium$f, probs = 0.95))),colour="grey")

df_complet %>% 
  ggplot(aes(x = school, y=P_month_est_low$f))+
  scale_y_continuous(labels = scales::percent_format(scale = 100), breaks = c(0,0.05, 0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))+
  xlab("Country") + 
  ylab("Monthly risk of infection)") +
  theme_bw2() +
  geom_boxplot(width=0.3, color="black", alpha=0.2, outlier.shape = NA) +
  geom_point(aes(x=1,y=unname(quantile(df_ch1$P_month_est_low$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=2,y=unname(quantile(df_ch2$P_month_est_low$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=3,y=unname(quantile(df_sa$P_month_est_low$f, probs = 0.95))),colour="grey") +
  geom_point(aes(x=4,y=unname(quantile(df_tz$P_month_est_low$f, probs = 0.95))),colour="grey")
```




